---
title: "Project R"
author: "Evgeniia"
date: "26 03 2021"
output: html_document
---

## Dataset
```{r dataset, echo = FALSE, message = FALSE, warning = FALSE}
library(ggplot2)



library(tidyverse)
review <- readr::read_csv('reviews_1.csv')
#summary(review)
review1 <- review %>%
  select(!X1)%>%
  rename(Stars = stars,Feedback = feedback, Gender = gender, Words = num_words,Name = name)
knitr::kable(review1[1:10, 1:5])
```
#### **Summary**
```{r dataset_summary, echo = FALSE, message = FALSE, warning = FALSE}
knitr::kable(summary(review1))
```
#### **Visualization**
```{r dataset_vis, echo = FALSE, message = FALSE, warning = FALSE}

vis <- review1 %>%
  ggplot(aes(x = Stars, y = Words)) +
  geom_jitter(aes(colour = Gender), alpha = 0.5,) +
  geom_hline(yintercept = mean(review1$Words, na.rm=T), col="black", linetype="dotted")+
  annotate("text", x = 2, y = mean(review1$Words, na.rm=T)-2, label="Average feedback length", col="black", size=3)+
  labs(x = "Stars", y = "Length of feedback (words)")+
  scale_x_continuous(breaks = c(1,2,3,4,5))+
  theme_gray() +
  theme(panel.background = element_rect(fill = "#dde6f0",
                                colour = "#dde6f0",))
  
  
vis

```

## Data analysis by gender


#### **Summary**
```{r summary1, echo = FALSE, message = FALSE, warning = FALSE}
#install.packages("psych")
library("psych")
library("dplyr")
summary <- review1 %>%
  group_by(Gender) %>%
  summarise(describe(Words))
knitr::kable(summary)


```



#### **Two Sample T-test**
```{r T-test, echo = FALSE, message = FALSE, warning = FALSE}
#review1 %>% 
  #filter(Gender == "M")
review2 <- review1 %>%
  slice_head(n = 530)
#review2
reviewFM <- review2 %>%
  filter(Gender %in% c("F","M"))
t.test(Words ~ Gender, data = reviewFM, paired = FALSE)

```






#### **Feedback length distribution by gender**

```{r Boxes, echo = FALSE, message = FALSE, warning = FALSE}
library(plotly)
fig <- plot_ly(review1, y = ~Words, color = ~Gender, type = "box")
fig <- fig %>% layout(paper_bgcolor = "white", plot_bgcolor = "dde6f0")
fig <- fig %>% layout(yaxis = list(title = 'Length of feedback (words)'), 
                      xaxis = list(title = 'Gender'))

fig
```







## Data analysis by stars
#### **Summary**
```{r summary2, echo = FALSE, message = FALSE, warning = FALSE}
summary1 <- review1 %>%
  group_by(Stars) %>%
  summarise(describe(Words))
knitr::kable(summary1)


```

#### **Feedback length distribution by stars**
```{r visual2, echo = FALSE, message = FALSE, warning = FALSE}

ggplot(data = review1) +
  (aes(color = Stars, fill = Stars, x = Stars, y = Words)) +
  geom_boxplot(alpha = 0.5, width = 40) +
  geom_jitter(alpha = 0.3, width=10, height=0) +
  #geom_hline(yintercept = mean(review1$Words, na.rm=T), col="white", linetype="dotted")+
  #annotate("text", x = 2, y = mean(review1$Words, na.rm=T)-2, label="Average feedback length", col="white", size=2)+
  scale_x_continuous(breaks = (NULL)) +
  coord_fixed() +
  facet_wrap(~Stars)+
  theme_minimal() +
  theme(panel.background = element_rect(fill = "#dde6f0",
                                        colour = "#dde6f0"))

```


#### **Analysis of variance ANOVA**

```{r Test, echo = FALSE, message = FALSE, warning = FALSE}
review_test <- review1 %>%
  mutate(Starsf = factor(Stars))
aov_model<- aov(Words ~ Starsf, review_test)
aov_model
summary(aov_model)
```

#### **Tukey HSD post hoc test**


```{r POst-hoc, echo = FALSE, message = FALSE, warning = FALSE}
TukeyHSD(aov_model)
 

```


#### **Mean feedback length by the number of stars**

```{r vis3, echo = FALSE, message = FALSE, warning = FALSE}

review1$Stars <- as.vector(review1$Stars)
review1$Words <- as.vector(review1$Words)


d <- aggregate(review1$Words, review1["Stars"], 
               mean, na.rm = T)

ggplot(d, aes(x=Stars, y = x))+
  geom_col(position = "dodge", alpha = 0.5, fill = "#0e3673")+
  scale_y_continuous(name = "Mean feedback length (woeds)") +
  theme(panel.background = element_rect(fill = "#dde6f0",
                                colour = "#dde6f0",))

```

#### **General visualization of feedback length depending on the gender and the number of stars**

```{r vis5, echo = FALSE, message = FALSE, warning = FALSE}

ggplot(data = review1) +
  (aes(x = Stars, y = Words, fill = Gender)) +
  geom_boxplot(aes(color = Gender), alpha = 0.6,width = 40) +
  geom_hline(yintercept = mean(review1$Words, na.rm=T), col="black", linetype="dotted")+
  annotate("text", x = 2, y = mean(review1$Words, na.rm=T)-2, label="Mean feedback length", col="black", size=2)+
  scale_x_continuous(breaks = (NULL)) +
  scale_y_continuous(name = "Feedback length (words)") +
  coord_fixed() +
  facet_wrap(~Stars)+
  theme_minimal() +
  theme(panel.background = element_rect(fill = "#dde6f0",
                                        colour = "#dde6f0",))



```

